Covariate analysis of ROSMAP RNASeq

### 2016-02-09 code/Rmd/ROSMAP_RNASeq.Rmd
Minor modifications

### Outliers detection
```{r decompse.normalise.data, fig.height=8, fig.width=8, results='asis'}
# Find principal components of expression to plot
PC <- prcomp(EXPR, scale.=T)

@@

COVARIATES.tmp = data.matrix(COVARIATES)
COVARIATES.tmp[is.na(COVARIATES.tmp)] = 0

tree = hclust(as.dist(t(EXPR)))
plotDendroAndColors(tree, 
                    colors = labels2colors(COVARIATES.tmp), 
                    dendroLabels = FALSE, 
                    abHeight = 0.80, 
                    main = "Sample dendrogram",
                    groupLabels = colnames(COVARIATES.tmp))
```

@@

### Clustering residual gene expression
```{r decompse.normalise.data1, fig.height=8, fig.width=8, results='asis'}
# Find principal components of expression to plot
PC <- prcomp(RESIDUAL.GENE_EXPRESSION[,-(1:2)], scale.=T)

@@

COVARIATES.tmp = data.matrix(COVARIATES)
COVARIATES.tmp[is.na(COVARIATES.tmp)] = 0

tree = hclust(as.dist(t(RESIDUAL.GENE_EXPRESSION[,-(1:2)])))
WGCNA::plotDendroAndColors(tree, 
                    colors = labels2colors(COVARIATES.tmp), 
                    dendroLabels = FALSE, 
                    abHeight = 0.80, 
                    main = "Sample dendrogram",
                    groupLabels = colnames(COVARIATES.tmp))
```

>>>>

### Outliers detection
```{r decompse.normalise.data1, fig.height=8, fig.width=8, results='asis'}
# Find principal components of expression to plot
PC <- prcomp(EXPR, scale.=T)

@@

COVARIATES.tmp = data.matrix(COVARIATES)
COVARIATES.tmp[is.na(COVARIATES.tmp)] = 0
```
```{r decompse.normalise.data2, fig.height=8, fig.width=16, results='asis'}
tree = hclust(as.dist(t(EXPR)))
plotDendroAndColors(tree, 
                    colors = labels2colors(COVARIATES.tmp), 
                    dendroLabels = FALSE, 
                    abHeight = 0.80, 
                    main = "Sample dendrogram",
                    groupLabels = colnames(COVARIATES.tmp))
dev.off()
```

@@

### Clustering residual gene expression
```{r decompse.normalise.data3, fig.height=8, fig.width=8, results='asis'}
# Find principal components of expression to plot
PC <- prcomp(RESIDUAL.GENE_EXPRESSION[,-(1:2)], scale.=T)

@@

COVARIATES.tmp = data.matrix(COVARIATES)
COVARIATES.tmp[is.na(COVARIATES.tmp)] = 0
```
```{r decompse.normalise.data4, fig.height=8, fig.width=16, results='asis'}
tree = hclust(as.dist(t(RESIDUAL.GENE_EXPRESSION[,-(1:2)])))
WGCNA::plotDendroAndColors(tree, 
                    colors = labels2colors(COVARIATES.tmp), 
                    dendroLabels = FALSE, 
                    abHeight = 0.80, 
                    main = "Sample dendrogram",
                    groupLabels = colnames(COVARIATES.tmp))
dev.off()
```
